{\it E}nKCF: Ensemble of Kernelized Correlation Filters for Object Tracking in High Speed

### 2017-05-30 bmvc_review.tex
Algorithm Place Modified
Algorithm Cleaned - Used a Better Format

\documentclass{bmvc2k}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools} % mathtools builds on and extends amsmath package
\usepackage{algorithm}		% http://ctan.org/pkg/algorithms
\usepackage{algpseudocode}	% http://ctan.org/pkg/algorithmicx% Include other packages here, before hyperref.
\usepackage{comment, url}
%% Enter your paper number here for the review copy
\bmvcreviewcopy{825}

@@

@@

\begin{algorithm}[h]
\small
	\caption{{\it E}nKCF Tracking Algorithm.}\label{alg:MKCF}
	\begin{algorithmic}[1]
	\State \textbf{Input} : Initial bounding box $x_{0}$, frame counter $fc$, scale filter frequency $n = 5$,
	\State \textbf{Output} : 
				\If{$fc\:\%\:n=0$} \Comment{Condition 1}
						\State Estimated Target State $x_{t} = (x_{t},y_{t},s_{t})$,
						Scale filter (\textit{target-only}) model $R_{s}$.
			     \EndIf
				\If{$fc\:\%\:n=1\:\:or\:\:fc\:\%\:n=2$}\Comment{Condition 2}
						\State Estimated Target State $x_{t} = (x_{t},y_{t},s_{t_1})$,
						Large Area Translation Filter model $R_{t}^{L}$.
				\EndIf
				\If{$fc\:\%\:n=3\:\:or\:\:fc\:\%\:n=4$}\Comment{Condition 3}
						\State Estimated Target State $x_{t} = (x_{t},y_{t},s_{t})$,
						Small Area Translation Filter model $R_{t}^{S}$.
				\EndIf
	\Procedure{track}{$x_{t-1},y_{t-1},s_{t-1}$} 
				\State // Translation Estimation
				\State Transit Particle Filter to the frame $t$ and compute the mean of prior pdf $x_{t} = (x_{t},y_{t},s_{t-1})$;
				\State // Translation Estimation
				\State Crop the ROI for the $R_{t}^{L}$, or $R_{t}^{S}$ given $x_{t}$
				and estimate translation ($x_{t}$,$y_{t}$) using $R_{t}^{L}$ (Condition 2) or $R_{t}^{S}$ (Condition 3),
				\State Skip translation estimation for $R_{s}$ (Condition 1);
				\State // Scale Estimation
			    \State Crop the ROI for the $R_{s}$ and estimate scale, $s_{t}$, using $R_{s}$ (Condition 1), 
				\State Scale pool for $R_{s}$ : $\lbrace1.05,1.0,1/1.05\rbrace$;
		        \State Skip it for $R_{t}^{L}$ and $R_{t}^{S}$ (Condition 1, and 2),
				\State // Update Translation
				\State Perform Importance Re-sampling (if necessary) for Particle Filter and compute the mean of posterior pdf $x_{t} = (x_{t},y_{t},s_{t})$;
			    \State // Model Update
			    \State Update $R_{t}^{S}$ (Condition 3);
			    \State Update $R_{t}^{L}$ (Condition 2);
			     \If{$PSR(y_{R_{s}}) \geq T_{R_{s}}$}
				\State Update $R_{s}$ (Condition 1);
			     \EndIf		
	\EndProcedure	
	\end{algorithmic}
\end{algorithm}

>>>>

\documentclass{bmvc2k}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools} % mathtools builds on and extends amsmath package
% \usepackage{algorithm}		% http://ctan.org/pkg/algorithms
\usepackage{algpseudocode}	% http://ctan.org/pkg/algorithmicx% Include other packages here, before hyperref.
\usepackage{comment, url}
\usepackage[ruled, vlined, linesnumbered]{algorithm2e}

%% Enter your paper number here for the review copy
\bmvcreviewcopy{825}

@@

\begin{algorithm}[h]
\small
\DontPrintSemicolon
\KwIn{ Initial bounding box $(x_{0},y_{0},s_{0})$, frame counter $fc$, scale filter frequency $n = 5$,}
\KwOut{	\uIf{$fc\:\%\:n=0$ (Condition 1)}
			{
				Estimated Target State $(x_{t},y_{t},s_{t})$,
				Scale filter (\textit{target-only}) model $R_{s}$.
			}			  
			 \ElseIf{$fc\:\%\:n=1\:\:or\:\:fc\:\%\:n=2$ (Condition 2)}
			 {
				Estimated Target State $(x_{t},y_{t},s_{t})$,
			  	Large Area Translation Filter model $R_{t}^{L}$.
			}			 
			 \Else (\textit{Condition 3})
			{			 
				 Estimated Target State $(x_{t},y_{t},s_{t})$,
				Small Area Translation Filter model $R_{t}^{S}$.				
			}	
		}
\SetKwBlock{Begin}{function}{end function}
\Begin($\text{track($x_{t-1},y_{t-1},s_{t-1}$) }$)
{
 	// \textit{Translation Estimation - Particle Filter} \\
	Transit Particle Filter to the frame $t$ and compute the mean of prior pdf $(x_{t},y_{t},s_{t-1})$ \\
     // \textit{Translation Estimation - Correlation Filter} \\
	Crop the ROI for the $R_{t}^{L}$ (Condition 2), or $R_{t}^{S}$ (Condition 3) given $(x_{t},y_{t})$ and estimate new position ($x_{t}$,$y_{t}$),\\
	// \textit{Scale Estimation - Correlation Filter}\\
	Crop the ROI for the $R_{s}$ and estimate scale, $s_{t}$ (Condition 1),\\ 
	Scale pool for $R_{s}$ : $\lbrace1.05,1.0,1/1.05\rbrace$,\\
	Skip it for $R_{t}^{L}$ and $R_{t}^{S}$ ($s_{t}$=$s_{t-1}$)\\
	// \textit{Update Translation - Particle Filter}\\
	Do Importance Re-sampling (if necessary) and compute the 
	mean of posterior pdf $(x_{t},y_{t})$\\
	// \textit{Model Update}\\
	Update $R_{t}^{S}$ (Condition 3),\\
	Update $R_{t}^{L}$ (Condition 2),\\
	\uIf{$PSR(y_{R_{s}}) \geq T_{R_{s}}$}{
		Update $R_{s}$ (Condition 1)}
  \label{endfor}
  \Return{($x_{t},y_{t},s_{t}$)}
}
\caption{{\it E}nKCF Tracking Algorithm}\label{costalgorithm}
\end{algorithm}

%\begin{algorithm}[h]
%\small
%	\caption{{\it E}nKCF Tracking Algorithm.}\label{alg:MKCF}
%	\begin{algorithmic}[1]
%	\State \textbf{Input} : Initial bounding box $x_{0}$, frame counter $fc$, scale filter frequency $n = 5$,
%	\State \textbf{Output} : 
%				\If{$fc\:\%\:n=0$} \Comment{Condition 1}
%						\State Estimated Target State $x_{t} = (x_{t},y_{t},s_{t})$,
%						Scale filter (\textit{target-only}) model $R_{s}$.
%			     \EndIf
%				\If{$fc\:\%\:n=1\:\:or\:\:fc\:\%\:n=2$}\Comment{Condition 2}
%						\State Estimated Target State $x_{t} = (x_{t},y_{t},s_{t})$,
%						Large Area Translation Filter model $R_{t}^{L}$.
%				\EndIf
%				\If{$fc\:\%\:n=3\:\:or\:\:fc\:\%\:n=4$}\Comment{Condition 3}
%						\State Estimated Target State $x_{t} = (x_{t},y_{t},s_{t})$,
%						Small Area Translation Filter model $R_{t}^{S}$.
%				\EndIf
%	\Procedure{track}{$x_{t-1},y_{t-1},s_{t-1}$} 
%				\State // Translation Estimation
%				\State Transit Particle Filter to the frame $t$ and compute the mean of prior pdf $x_{t} = (x_{t},y_{t},s_{t-1})$;
%				\State // Translation Estimation
%				\State Crop the ROI for the $R_{t}^{L}$, or $R_{t}^{S}$ given $x_{t}$
%				and estimate translation ($x_{t}$,$y_{t}$),
%				\State Skip translation estimation for $R_{s}$ (Condition 1);
%				\State // Scale Estimation
%			    \State Crop the ROI for the $R_{s}$ and estimate scale, $s_{t}$, using $R_{s}$ (Condition 1), 
%				\State Scale pool for $R_{s}$ : $\lbrace1.05,1.0,1/1.05\rbrace$;
%		        \State Skip it for $R_{t}^{L}$ and $R_{t}^{S}$ ($s_{t}$=$s_{t-1}$),
%				\State // Update Translation
%				\State Perform Importance Re-sampling (if necessary) for Particle Filter and compute the mean of posterior pdf $x_{t} = (x_{t},y_{t},s_{t})$;
%			    \State // Model Update
%			    \State Update $R_{t}^{S}$ (Condition 3);
%			    \State Update $R_{t}^{L}$ (Condition 2);
%			     \If{$PSR(y_{R_{s}}) \geq T_{R_{s}}$}
%				\State Update $R_{s}$ (Condition 1);
%			     \EndIf		
%	\EndProcedure	
%	\end{algorithmic}
%\end{algorithm}

@@
